\documentclass[a4paper,english]{article}
\usepackage{cleveref}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[lining]{ebgaramond}

\title{EDAG01 --- Project}
\author{Henrik Vester (\texttt{he5834ve-s})}

\begin{document}

\maketitle

The purpose of this short report is to analyze the \texttt{intopt} program written as part of the course load for the EDAG01 Efficient C course given at the Faculty of Engineering, Lund University. The \texttt{intopt} program is able to solve linear programming problems using the simplex algorithm, as well as integer linear programming problems with the addition of the branch-and-bound algorithm.

% What takes time in the program? Explain using profiling information

In order to see what it is that takes the most time in the program, a profiler is used --- in this case \texttt{operf}. The following command is executed:

\begin{verbatim}
operf -e CYCLES:100000:0:0:1 ./a.out < input
\end{verbatim}

The result of the command

\begin{verbatim}
opreport -t 1 -l -g a.out
\end{verbatim}

is used to see which functions the program spends the most time in. The most time-consuming function is \texttt{pivot}. See \cref{section:opreport} for the output.

% Which optimizations are most useful? (Probably not needed)

% What can you do to improve performance further?

No hand-written optimizations have been done for this program, with the score of {\color{red}XXXX} still being well above the minimnum 80. If such optimizations were to take place, the most logical place to start would be the \texttt{pivot} function, since it is the most time-consuming. \texttt{pivot} has a total of five \texttt{for} loops, which could probably benefit greatly from vectorization. For each of the five loops in \texttt{pivot}, we would have to ensure that all array accesses are kept contiguous, and when that is the case, going through the generated assembly code and check that vectorization instructions have appeared.

\appendix

\section{Output of \texttt{opreport}}\label{section:opreport}

{
\scriptsize
\begin{verbatim}
Using /home/he5834ve-s/lab4/oprofile_data/samples/ for samples directory.
CPU: ppc64 POWER8, speed 3491 MHz (estimated)
Counted CYCLES events (Cycles) with a unit mask of 0x00 (No unit mask) count 100000
samples  %        linenr info                 image name               symbol name
11       34.3750  (no location information)   a.out                    pivot
3         9.3750  isoc99_scanf.c:27           libc-2.27.so             __isoc99_scanf
3         9.3750  vfprintf.c:1244             libc-2.27.so             vfprintf@@GLIBC_2.17
2         6.2500  vfscanf.c:280               libc-2.27.so             _IO_vfscanf@@GLIBC_2.17
2         6.2500  printf_fp.c:213             libc-2.27.so             __GI___printf_fp_l
2         6.2500  putchar.c:25                libc-2.27.so             putchar
1         3.1250  (no location information)   a.out                    xsimplex
1         3.1250  dl-reloc.c:148              ld-2.27.so               _dl_relocate_object
1         3.1250  dl-lookup.c:936             ld-2.27.so               _dl_setup_hash
1         3.1250  dl-lookup.c:338             ld-2.27.so               do_lookup_x
1         3.1250  (no location information)   libc-2.27.so             00000037.plt_call.__GI_memcpy
1         3.1250  memcpy.S:38                 libc-2.27.so             __memcpy_power7
1         3.1250  dl-addr.c:126               libc-2.27.so             _dl_addr
1         3.1250  _itoa.c:165                 libc-2.27.so             _itoa_word
1         3.1250  printf_fp.c:167             libc-2.27.so             hack_digit
\end{verbatim}
}


\end{document}